Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-11-12 writing/ehp_introduction.tex
Work some more on draft

Recently, several major tropical cyclones have hit \ac{US} cities, including
Hurricanes Harvey, Irma, and Maria in 2017~\parencite{blake20182017} and
Hurricanes Florence and Michael in 2018 \parencite{avila20192018}. Researchers
are exploring how these storms impacted human health
(e.g.,~\cite{santos2018use, rivera2018estimating, santos2018differential,
grineski2019impact, issa2018deaths, tanz2019notes, paul2019brief}), including
through projects funded by \ac{NIH} Rapid Response
grants~\parencite{nihreporter}. These projects will add to evidence
characterizing how hurricanes impact human health, including evidence from
multi-year studies based on fatality data from post-disaster
surveillance~\parencite{rappaport2000, rappaport2014fatalities,
rappaport2016fatalities, czajkowski2010fatal, czajkowski2011, moore2012}.

For several types of climate-related disasters---including heat waves, floods,
and wildfires---research based on post-disaster surveillance data has been
richly supplemented by studies analyzing trends in community-wide
administrative or vital data, including time series or case-crossover studies
(e.g.,~\cite{anderson2010heat, son2012impact, haikerwal2015impact,
liu2017wildfire, milojevic2017mental}).  These studies typically compare the
rate of a health outcome in a community during a disaster or disasters to rates
during comparable non-disaster periods.  While these studies cannot attribute
specific cases (e.g., a specific person's death) to a disaster, they can help
characterize the community-wide change in health risk during disasters, and can
help capture impacts that might be missed or underestimated in post-disaster
surveillance.  In many cases, these studies analyze multi-year, multi-community
data, allowing them to estimate average associations over many disasters and to
explore how a disaster's characteristics, or the characteristics of the
community it hits, modify associated health risk (e.g.,~\cite{anderson2010heat,
son2012impact, liu2017wildfire}).  Some studies have begun to use this approach
to study the health impacts of tropical cyclones, including several studies of
Hurricane Maria (e.g.,~\cite{santos2018use, santos2018differential}), Hurricane
Sandy (e.g.,~\cite{kim2016, mongin2017, swerdel2014}), and the 2004 hurricane
season in Florida~\parencite{mckinney2011}.  However, to expand this approach
to study longer time periods for large sets of communities, researchers must be
able to assess exposure to tropical cyclones consistently and comparably across
storms, years, and communities.

The \ac{NHC} publishes a ``Best Tracks'' dataset that is considered the gold
standard for Atlantic-basin tropical cyclone tracks.  It records the central
position of a tropical cyclone every six hours, as well as the storm's minimum
central pressure and maximum wind speed.  This data is openly available through
the \ac{HURDAT2}, a post-storm assessment that incorporates data from several
sources, including satellite data and, when available, aircraft reconnaissance
data~\parencite{landsea2013, jarvinen1988}.  With this data, it is
straightforward to measure whether a community was in the direct path, or
within a certain distance of the path, of a storm. Some studies have indeed
used this data within epidemiological studies to assess tropical cyclone
exposure based on whether a storm's track passed through a community or how
near the storm's central track came to the community (e.g.,~\cite{currie2013,
kinney2008, caillouet2008increase}).

When epidemiological studies assess exposure to a tropical cyclone using, as a
proxy measurement, how close the storm came to a community, they may
misclassify exposure~\parencite{grabich2015measuring}. While a number of
tropical cyclone hazards are strongly associated with distance from the
tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like heavy rainfall,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.  Further, when studies use
distance from the storm's track to assess exposure, they often use the same
buffer constraints on each side of the tropical cyclone track
(e.g.,~\cite{czajkowski2011, kinney2008, currie2013}).  However, the forces of
a tropical cyclone tend to be distributed around its center non-symmetrically.
Extreme winds are more common to the track's right, where counter-clockwise
cyclonic winds move in concert with the tropical cyclone's forward
motion~\parencite{halverson2015}, and almost all of the fatal tornadoes
associated with \ac{US} tropical cyclones between~1995 and~2009 occurred to the
right of the tropical cyclone's track, mostly in the storm's right front
quadrant~\parencite{moore2012}. Rain, conversely, is often heaviest to the left
of the track, especially when the tropical cyclone interacts with other weather
systems~\parencite{atallah2003, atallah2007, zhu2013variations} or undergoes an
extratropical transition~\parencite{elsberry2002}.

The multi-hazard nature of tropical cyclones therefore makes it hard to assess
exposure based on how close the storm's central
track came to the community.  While other approaches have been developed to
incorporate storm hazards, particulary wind, into exposure assessment (e.g.,
\cite{grabich2015measuring, zandbergen2009, czajkowski2011}), there is not yet
a standard approach, and when different studies use different datasets or storm
hazards when assessing storm exposure, it becomes difficult to compare and
aggregate findings from different studies.

To help epidemiological researchers assess exposure to tropical cyclones, we
developed an open-source dataset~\parencite{hurricaneexposure}.  These data
cover all counties in states in the eastern half of the \ac{US} over multiple
years and include five metrics characterizing exposure to tropical cyclones
(Table~\ref{tab:exposuremetrics}): (1)~closest distance the storm's central
track came to the county's center (a proxy measurement of storm exposure used
in some previous studies); (2)~maximum sustained wind speed at the county's
center over the course of the storm; (3)~cumulative rainfall in the county over
the course of the storm; (4)~flood events in the county associated with the
storm; and (5)~tornado events in the county associated with the storm.  We
aggregated these data at the county level since data on many potential impacts
are available at county-level aggregations (e.g., direct hurricane-related
deaths~\parencite{czajkowski2011}; birth outcomes~\parencite{grabich2015,
grabich2015measuring}; autism prevalence~\parencite{kinney2008}) and since
decisions and policies to prepare for, and respond to, tropical cyclones are
often undertaken at the county level~\parencite{zandbergen2009, rappaport2000}.
We also wrote functions to explore and map this data and to link it
with county-level health data~\parencite{hurricaneexposuredata}

Here, we describe how we developed this dataset and explore how its
measurements compare to other data that could be used to characterize tropical
cyclone hazards in the context of epidemiological research. Further, we expand
on previous research that investigated methods to measure exposure to tropical
cyclones for epidemiological research~\parencite{grabich2015measuring}.  The
previous study investigated differences in which communities were assessed as
exposed to tropical cyclones during the 2004 hurricane season in Florida,
depending on whether exposure assessment was based on distance to the storm's
track or used a metric incorporating storm-related winds within the county
during the storm.  They found important differences across methods of assessing
storm exposure, concluding that a study may be prone to bias from exposure
misclassification if distance to the storm track is used as a proxy measurement
for exposure assessment~\parencite{grabich2015measuring}.  Here we expand to
investigate this question across all counties in states in the eastern half of
the \ac{US} over multiple storms and years.  Further, we investigate patterns
in exposure classification based on other metrics of storm-related
hazards---rainfall, flooding, and tornadoes---that are important to
characterize to improve understanding of the inland health impacts of tropical
cyclones~\parencite{czajkowski2011, moore2012}. These results can help
epidemiologists design studies and plan statistical analysis for multi-year,
multi-community studies that investigate changes in community-wide rates of
health outcomes during exposure to the hazards brought by tropical cyclones,
including counties inland from a storm's landfall.

>>>>

Hurricanes and other tropical cyclones can severely impact human health in
\ac{US} communities, and some of these impacts have been characterized through
multi-year studies based on fatality data from post-disaster
surveillance~\parencite{rappaport2000, rappaport2014fatalities,
rappaport2016fatalities, czajkowski2010fatal, czajkowski2011, moore2012}.  For
several types of climate-related disasters---including heat waves, floods, and
wildfires---research based on post-disaster surveillance data has been richly
supplemented by studies analyzing trends in community-wide administrative or
vital data, including time series or case-crossover studies
(e.g.,~\cite{anderson2010heat, son2012impact, haikerwal2015impact,
liu2017wildfire, milojevic2017mental}).  These studies typically compare the
rate of a health outcome in a community during a disaster to rates during
comparable non-disaster periods.  While these studies cannot attribute specific
cases (e.g., a specific person's death) to a disaster, they can help
characterize the community-wide change in health risk during disasters and
capture impacts that might be missed or underestimated in post-disaster
surveillance.  In many cases, these studies analyze multi-year, multi-community
data, allowing them to estimate average associations over many disasters and to
explore how a disaster's characteristics, or the characteristics of the
community it hits, modify associated health risks (e.g.,~\cite{anderson2010heat,
son2012impact, liu2017wildfire}).  Some studies have begun to use this approach
to study the health impacts of tropical cyclones, including several studies of
Hurricane Maria (e.g.,~\cite{santos2018use, santos2018differential}), Hurricane
Sandy (e.g.,~\cite{kim2016, mongin2017, swerdel2014}), and the 2004 hurricane
season in Florida~\parencite{mckinney2011}.  However, to expand this approach
to study longer time periods for large sets of communities, researchers must be
able to assess exposure to tropical cyclones consistently and comparably across
storms, years, and communities.

The \ac{NHC} publishes a ``Best Tracks'' dataset that is considered the gold
standard for Atlantic-basin tropical cyclone tracks.  It records the central
position of a tropical cyclone every six hours, as well as the storm's minimum
central pressure and maximum wind speed.  These data are openly available
through the \ac{HURDAT2}, a post-storm assessment that incorporates data from
several sources, including satellite data and, when available, aircraft
reconnaissance data~\parencite{landsea2013, jarvinen1988}.  With these data, it
is straightforward to measure whether a community was in the direct path, or
within a certain distance of the central track, of a storm, as some previous
epidemiological studies have done to assess exposure to a tropical storm
(e.g.,~\cite{currie2013, kinney2008, caillouet2008increase}).

However, when epidemiological studies assess exposure to a tropical cyclone
using, as a proxy measurement, how close the storm came to a community, they
may misclassify exposure~\parencite{grabich2015measuring}. While a number of
tropical cyclone hazards are strongly associated with distance from the
tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like heavy rainfall,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.  Further, when studies use
distance from the storm's track to assess exposure, they often use the same
buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  Extreme
winds are more common to the track's right, where counter-clockwise cyclonic
winds move in concert with the tropical cyclone's forward
motion~\parencite{halverson2015}, and almost all of the fatal tornadoes
associated with \ac{US} tropical cyclones between~1995 and~2009 occurred to the
right of the tropical cyclone's track~\parencite{moore2012}. Rain, conversely,
is often heaviest to the left of the track, especially when the tropical
cyclone interacts with other weather systems~\parencite{atallah2003,
atallah2007, zhu2013variations} or undergoes an extratropical
transition~\parencite{elsberry2002}.  The multi-hazard nature of tropical
cyclones therefore makes it hard to assess exposure based on how close the
storm's central track came to the community.  While other approaches have been
developed to incorporate storm hazards, particulary wind, into exposure
assessment (e.g., \cite{grabich2015measuring, zandbergen2009, czajkowski2011}),
there is not yet a standard approach, and when different studies use different
datasets or storm hazards when assessing storm exposure, it becomes difficult
to compare and aggregate findings from different studies.

To help epidemiological researchers assess exposure to tropical cyclones, we
developed an open-source dataset~\parencite{hurricaneexposure}.  These data
cover all counties in states in the eastern half of the \ac{US} over multiple
years and include five metrics characterizing exposure to tropical cyclones
(Table~\ref{tab:exposuremetrics}): (1)~closest distance the storm's central
track came to the county's center (a proxy measurement of storm exposure used
in some previous studies); (2)~maximum sustained wind speed at the county's
center over the course of the storm; (3)~cumulative rainfall in the county over
the course of the storm; (4)~flooding in the county
concurrent with the storm; and (5)~tornadoes in the county
concurrent with the storm.  We aggregated these data at the county level since
data for epidemiological studies are often available at county-level
aggregations (e.g., direct hurricane-related deaths~\parencite{czajkowski2011};
birth outcomes~\parencite{grabich2015, grabich2015measuring}; autism
prevalence~\parencite{kinney2008}) and since decisions and policies to prepare
for, and respond to, tropical cyclones are often undertaken at the county
level~\parencite{zandbergen2009, rappaport2000}.  We also wrote functions to
explore and map these data and to link it with county-level health
data~\parencite{hurricaneexposuredata}

Here, we describe how we developed this dataset and explore how its
measurements compare to other data that could be used to characterize tropical
cyclone hazards for epidemiological research. Further, we expand
on previous research that investigated methods to measure exposure to tropical
cyclones for epidemiological research~\parencite{grabich2015measuring}.  The
previous study investigated differences in which communities were assessed as
exposed to tropical cyclones during the 2004 hurricane season in Florida,
depending on whether exposure assessment was based on distance to the storm's
track or used a metric incorporating storm-related winds within the county
during the storm.  They found important differences across methods of assessing
storm exposure, concluding that a study may be prone to bias from exposure
misclassification if distance to the storm track is used as a proxy measurement
for exposure assessment~\parencite{grabich2015measuring}.  Here we expand to
investigate this question across a large set of counties and storm seasons.
Further, we investigate patterns in exposure classification based on other
metrics of storm-related hazards---rainfall, flooding, and tornadoes---that are
important to characterize to improve understanding of the inland health impacts
of tropical cyclones~\parencite{czajkowski2011, moore2012}. These results can
help epidemiologists design studies and plan statistical analysis for
multi-year, multi-community studies that investigate changes in community-wide
rates of health outcomes during exposure to the hazards brought by tropical
cyclones, including counties inland from a storm's landfall.

### 2019-11-12 writing/ehp_methods.tex
Work some more on draft

We aggregated data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}) as of the~2010 \ac{US} Decennial Census. We
included all tracked land-falling or near-land Atlantic-basin tropical cyclones
between~1988 and~2015 by covering all 136 storms in \ac{HURDAT2}
\parencite{landsea2013} that came within~250 \si{\kilo\metre} of at least one
eastern \ac{US} county in this period (Figure~\ref{fig:hurrtracks}).

@@

We first measured how close each storm came to each county. We used tracking
data from \ac{HURDAT2}, which records the storm center's position every~6
\si{\hour} (at the synoptic times of 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am
\ac{UTC}), and interpolated this position to~15-\si{\minute} intervals using
natural cubic splines~\parencite{hurricaneexposure}. At each~15-\si{\minute}
interval, we measured the distance between the storm's center and each county's
population mean center~\parencite{bivand2013applied, countycenters}. We took
the minimum for each county as a measure of how close the storm came to the
county.  We also recorded the time the storm came closest to each county, which
we later used to link observed data on precipitation, flooding, and tornadoes
to the storm.  To allow matching with data recorded in local time (e.g., health
data), we converted these times from \ac{UTC} to local
time~\parencite{countytimezones}.

@@

We based storm rainfall measurements on precipitation data files from the
\ac{NLDAS-2} re-analysis dataset, which is available for the continental
\ac{US}~\parencite{rui2013nldas}. We used data that were previously aggregated
from this re-analysis dataset to the county level by two of the coauthors
(Al-Hamdan and Crosson) for the Centers for Disease Control and Prevention's
\ac{WONDER} database \parencite{cdcwonder, alhamdan2014environmental}. To
create this aggregated data originally, these coauthors took hourly
precipitation measurements in the \ac{NLDAS-2} precipitation files, which are
given at~1/8\si{\degree} grid points across the continential \ac{US}, and
summed them by day for each grid point.  This created a daily precipitation
total for each grid point; these were then averaged for all grid points within
a county's~1990 \ac{US} Census boundaries~\parencite{alhamdan2014environmental,
cdcwonder}. This process generated daily county-level precipitation estimates
for each continental \ac{US} county for 1988\,--\,2011 \parencite{cdcwonder}.
We matched these county-level daily measurements by date with storm tracks,
using for each county and storm the date when the storm was closest to the
county. Given the location of storm-affected counties and the typical timing of
tropical cyclones, these precipitation measures primarily represent rainfall,
although occasionally they may represent snowfall or other types of
precipitation.

In the open-source data~\parencite{hurricaneexposuredata}, we provide
precipitation values at a daily resolution for each county for the period from
five days before to three days after each storm's closest approach to the
county.  In the software that we published in association with this
data~\parencite{hurricaneexposure}, we provide functionality to aggregate these
daily values to create cumulative precipitation estimates for custom windows
around the date of the storm's closest approach to the county. For example, a
user could determine precipitation only on the day the storm was closest to
each county, but could also determine the cumulative rainfall for a more
extended period, like from three days before to three days after the storm's
closest approach. For the analysis of binary exposure classifications in this
study, we calculated storm-associated rainfall as the sum of precipitation from
two days before the storm's closest approach to the county to one day after.

@@

To create a dataset of county-level maximum sustained winds during historical
tropical cyclones, we modeled maximum sustained wind speeds at each county's
population mean center~\parencite{countycenters} using a wind speed model based
on results from Willoughby~\parencite{willoughby2006parametric}. For each
storm, we modeled the maximum ground-level sustained wind speed that the storm
generated at each county center for each~15-\si{\minute} increment throughout
the storm tracking period. We used a double exponential wind speed model with
inputs for the storm's forward speed, direction, and maximum wind
speed~\parencite{willoughby2006parametric, stormwindmodel}, incorporating the
asymmetry in wind speeds around the tropical cyclone center that results from
the storm's forward movement~\parencite{phadke2003modeling}. From these
15-\si{\minute} interval estimates, we identified the maximum sustained surface
wind speed in each county during each storm.

@@

We interpolated the wind radii data to~15-\si{\minute} increments and
classified a county as exposed to winds in a given wind speed category if its
population mean center was within~85\% of the maximum radius for that wind
speed in that quadrant of the storm. The~85\% adjustment is based on previous
research that found that this ratio helps capture average wind extents within a
quadrant from these maximum wind radii \parencite{knaff2016using}.  We compared
these wind radii-based estimates of county-level maximum sustained surface
winds during a storm with the modeled wind speed estimates, comparing all study
storms since 2004 for which at least one study county experienced sustained
winds of~$\ge$34 \si{\knot} based on the \ac{HURDAT2} wind radii. For each of
these storms, we calculated the percent of study counties that were classified
in the same wind speed category based on both data sources.

@@

To identify flood- and tornado-based tropical cyclone exposures in \ac{US}
counties, we used event listings from the National Oceanic and Atmospheric
Administration (NOAA)'s Storm Event Database~\parencite{stormevents}. While
this database has recorded storm data since~1950, its coverage changed
substantially in~1996 to cover a more types of storm
events~\parencite{stormevents}. We therefore only considered these metrics of
hurricane exposure for tropical cyclones in~1996 and later.

@@

The tornado observations from this dataset form a traditional tornado event
database for the \ac{US}, and so we did not further validate
the tornado event data. It is difficult to characterize flooding at the county
level because flooding can be very localized and can be triggered by a variety
of causes. To investigate the extent to which the NOAA flood event listings
capture extremes that might be identified with other flooding data sources, we
investigated a sample of study counties, comparing the flood event data during
tropical storms with streamflow measurements at \ac{US} Geological Survey
county streamflow gages \parencite{usgsgages, countyfloods, dataRetrieval}.

We considered nine study counties, selecting counties geographically spread
through storm-prone areas of the eastern \ac{US} and with multiple streamflow
gages reporting data during events. The sample counties were: Baltimore County,
MD; Bergen County, NJ; Escambia County, FL; Fairfield County, CT; Fulton
County, GA; Harris County, TX; Mobile County, AL; Montgomery County, PL; and
Wake County, NC. For each county, we first identified all streamflow gages in
the county with complete data for Jan.~1~1996\,--\,Dec.~31,~2015. If a storm
did not come within~500~\si{\kilo\metre} of a county, it was excluded from this
analysis, but all other study storms were considered.

For each storm and county, we summed streamflow measurements across all county
gages to generate daily totals for the five-day window around the storm's
closest approach. We took the maximum of these daily streamflow totals as a
measure of the county's maximum daily streamflow during that storm. We also
calculated the percent of streamflow gages in the county with a daily
streamflow that exceeded a threshold of flooding (the streamgage's median value
for annual peak flow~\parencite{countyfloods}) on any day during the five-day
window. We investigated how these measurements varied between storms with
associated flood events listed in the NOAA Storm Events data versus storms without an
event listing for the county, to explore if storms with flood event listings
tended to be associated with higher streamflow at gages within the county.

@@

In our open-source data, we provide continuous measurements of three exposure
metrics: closest distance of each storm to each county, maximum sustained winds
at the county center, and cumulative rainfall. However, epidemiologic studies
of tropical cyclones often use a binary exposure classification (``exposed''
versus ``unexposed'') to assess storm-related health risks, and so we
explored patterns in storm exposure based on binary clasifications of
these exposure metrics.

@@

Next, we investigated how well exposure assessment agreed across 
these metrics. For each storm we investigated the degree to which the 
set of counties assessed as exposed based on one metric overlapped with the set
assessed as exposed based on each other metric, including a metric that used
distance of a county from the storm track as a proxy for exposure to storm hazards. 
We calculated the within-storm
Jaccard index ($J_s$)~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics, which measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same set of counties as exposed to the
tropical cyclone. We measured these values for all study storms that affected a
large number of eastern \ac{US} counties (those storms with 100 or more
counties classified as exposed by at least one of the exposure metrics)
during the years when all exposure data were available (1996\,--\,2011).

>>>>

We aggregated data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}). We
included all tracked land-falling or near-land Atlantic-basin tropical cyclones
between~1988 and~2015 by covering all 136 storms in \ac{HURDAT2}
\parencite{landsea2013} that came within~250 \si{\kilo\metre} of at least one
eastern \ac{US} county in this period (the tracks of the study storms are shown in 
Figure~\ref{fig:hurrtracks}).

@@

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at the synoptic times of 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}, and
interpolated this position to~15-\si{\minute} intervals using natural cubic
splines~\parencite{hurricaneexposure}. At each~15-\si{\minute} interval, we
measured the distance between the storm's center and each county's population
mean center~\parencite{bivand2013applied, countycenters}. We took the minimum
distance for each county as a measure of how close the storm came to the
county.  We also recorded the time the storm came closest to each county, which
we later used to link observed data on precipitation, flooding, and tornadoes
to the storm.  To allow matching with data recorded in local time (e.g., health
data), we converted these times from \ac{UTC} to local
time~\parencite{countytimezones}.

@@

We based storm rainfall measurements on precipitation data files from the
\ac{NLDAS-2} re-analysis dataset, which is available for the continental
\ac{US}~\parencite{rui2013nldas}. We used data that were previously aggregated
from this re-analysis dataset to the county level by two of the coauthors
(Al-Hamdan and Crosson) for the Centers for Disease Control and Prevention's
\ac{WONDER} database \parencite{cdcwonder, alhamdan2014environmental}. To
create this aggregated data, these coauthors took hourly precipitation
measurements in the \ac{NLDAS-2} precipitation files, which are given
at~1/8\si{\degree} grid points across the continential \ac{US}, and summed them
by day for each grid point.  This created a daily precipitation total for each
grid point; these were then averaged for all grid points within a county's~1990
\ac{US} Census boundaries~\parencite{alhamdan2014environmental, cdcwonder}.
This process generated daily county-level precipitation estimates for each
continental \ac{US} county for 1988\,--\,2011 \parencite{cdcwonder}.  We
matched these county-level daily measurements by date with storm tracks, using
the date when the storm was closest to each county. Given the location of
storm-affected counties and the typical timing of tropical cyclones, these
precipitation measures primarily represent rainfall, although occasionally they
may represent snowfall or other types of precipitation.

In the open-source data~\parencite{hurricaneexposuredata}, we provide
precipitation values at a daily resolution for each county for the period from
five days before to three days after each storm's closest approach to the
county.  In the software that we published in association with this
data~\parencite{hurricaneexposure}, we provide functionality to aggregate these
daily values to create cumulative precipitation estimates for custom windows
around the date of the storm's closest approach to the county. For example, a
user could determine precipitation only on the day the storm was closest to
each county, but could also determine the cumulative rainfall for a more
extended period, like from two days before to two days after the storm's
closest approach. For the analysis of binary exposure classifications in this
study, we calculated storm-associated rainfall as the sum of precipitation from
two days before the storm's closest approach to the county to one day after.

@@

To create a dataset of county-level maximum sustained winds during historical
tropical cyclones, we modeled maximum sustained wind speeds at each county's
population mean center~\parencite{countycenters} using a wind speed model based
on results from Willoughby~\parencite{willoughby2006parametric}. For each
storm, we modeled the maximum ground-level sustained wind speed that the storm
generated at each county center for each~15-\si{\minute} increment throughout
the storm tracking period. We used a double exponential wind speed model with
inputs for the storm's forward speed, direction, and maximum wind
speed~\parencite{willoughby2006parametric, stormwindmodel}, incorporating the
asymmetry in wind speeds around the tropical cyclone center that results from
the storm's forward movement~\parencite{phadke2003modeling}. From these
15-\si{\minute} interval estimates, we identified the maximum sustained surface
wind speed in each county over the course of each storm.

@@

We interpolated the wind radii data to~15-\si{\minute} increments and
classified a county as exposed to winds in a given wind speed category if its
population mean center was within~85\% of the maximum radius for that wind
speed in that quadrant of the storm. The~85\% adjustment is based on previous
research that found that this ratio helps capture average wind extents within a
quadrant from these maximum wind radii \parencite{knaff2016using}.  We compared
these wind radii--based estimates of county-level maximum sustained surface
winds during a storm with the modeled wind speed estimates, comparing all study
storms since 2004 for which at least one study county experienced sustained
winds of~$\ge$34 \si{\knot} (based on the \ac{HURDAT2} wind radii). For each of
these storms, we calculated the percent of study counties that were classified
in the same wind speed category based on both data sources.

@@

To identify flood- and tornado-based tropical cyclone exposures in \ac{US}
counties, we matched storm tracks with event listings from the National Oceanic
and Atmospheric Administration (NOAA)'s Storm Event
Database~\parencite{stormevents}. While this database has recorded storm data
since~1950, its coverage changed substantially in~1996 to cover a more types of
storm events~\parencite{stormevents}. We therefore only considered these
metrics of hurricane exposure for tropical cyclones in~1996 and later.

@@

The tornado observations from this dataset form a traditional tornado event
database for the \ac{US}, and so we did not further validate
the tornado event data. It is difficult to characterize flooding at the county
level because flooding can be very localized and can be triggered by a variety
of causes. To investigate the extent to which the NOAA flood event listings
capture extremes that might be identified with other flooding data sources, we
investigated a sample of study counties, comparing the flood event data during
tropical storms with streamflow measurements at \ac{US} Geological Survey
county streamflow gages \parencite{usgsgages, countyfloods, dataRetrieval}.  
We considered nine study counties, selecting counties geographically spread
through storm-prone areas of the eastern \ac{US} and with multiple streamflow
gages reporting data during events. The sample counties were: Baltimore County,
MD; Bergen County, NJ; Escambia County, FL; Fairfield County, CT; Fulton
County, GA; Harris County, TX; Mobile County, AL; Montgomery County, PL; and
Wake County, NC. For each county, we first identified all streamflow gages in
the county with complete data for Jan.~1~1996\,--\,Dec.~31,~2015. If a storm
did not come within~500~\si{\kilo\metre} of a county, it was excluded from this
analysis, but all other study storms were considered. 
For each storm and county, we summed streamflow measurements across all county
gages to generate daily totals for the five-day window around the storm's
closest approach. We took the maximum of these daily streamflow totals as a
measure of the county's maximum daily streamflow during that storm. We also
calculated the percent of streamflow gages in the county with a daily
streamflow that exceeded a threshold of flooding (the streamgage's median value
for annual peak flow) on any day during the five-day
window. We investigated how these measurements varied between storms with
associated flood events listings versus storms without an
event listing for the county, to explore if storms with flood event listings
tended to be associated with higher streamflow at gages within the county.

@@

In our open-source data, we provide continuous measurements of some of the
exposure metrics: closest distance of each storm to each county, maximum
sustained winds at the county center, and cumulative rainfall. However,
epidemiologic studies of tropical cyclones often use a binary exposure
classification (``exposed'' versus ``unexposed'') to assess storm-related
health risks, and so we explored patterns in storm exposure based on binary
clasifications of these exposure metrics.

@@

Next, we investigated how well exposure assessment agreed across 
these metrics. For each storm we investigated the degree to which the 
set of counties assessed as exposed based on one metric overlapped with the set
assessed as exposed based on each other metric, including a metric that used
distance of a county from the storm track as a proxy for exposure to storm hazards. 
We calculated the within-storm
Jaccard index ($J_s$)~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics. This measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same set of counties as exposed to the
tropical cyclone. We calculated these values for all study storms that affected
$\ge$100 study counties (based on at least one exposure metric) during the
years when all exposure data were available (1996\,--\,2011).
